MINOS Handover Plots

### 2024-02-05 minos/validation/cross_validation_default.Rmd

# SF_12

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
multi_year_boxplots(raw, cv, 'SF_12')
snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2015, 2017, 2019, 2021))
q_q_comparison(raw, cv, 'SF_12')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2015)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2017)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2019)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2021)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

@@

>>>>

# SF_12_MCS

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_MCS')
multi_year_boxplots(raw, cv, 'SF_12_MCS')
snapshot_OP_plots(raw, cv, 'SF_12_MCS', target.years = c(2015, 2017, 2019, 2021))
q_q_comparison(raw, cv, 'SF_12_MCS')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2015)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2017)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2019)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2021)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

# SF_12_PCS

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_PCS')
multi_year_boxplots(raw, cv, 'SF_12_PCS')
snapshot_OP_plots(raw, cv, 'SF_12_PCS', target.years = c(2015, 2017, 2019, 2021))
q_q_comparison(raw, cv, 'SF_12_PCS')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2015)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2017)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2019)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_PCS', 
                                 target.year = 2021)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

@@

# Alcohol

```{r}
alc.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'auditc')

cv_ordinal_plots(pivoted.df = alc.pivoted, 
                 var = 'auditc',
                 save = FALSE)
rm(alc.pivoted)
```

# Physical Activity

```{r}
active.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'active')

cv_ordinal_plots(pivoted.df = active.pivoted, 
                 var = 'active',
                 save = FALSE)
rm(active.pivoted)
```

# Material Deprivation

```{r}
matdep.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'matdep')

cv_ordinal_plots(pivoted.df = matdep.pivoted, 
                 var = 'matdep',
                 save = FALSE)
rm(matdep.pivoted)
```

# Chronic Disease

```{r}
chron_disease.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'chron_disease')

cv_ordinal_plots(pivoted.df = chron_disease.pivoted, 
                 var = 'chron_disease',
                 save = FALSE)
rm(chron_disease.pivoted)
```

### 2024-02-05 minos/validation/handovers.Rmd

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

sf12.spag <- rbind(raw.sf12, base.sf12)

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```

@@

# Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.nut2 <- raw.dat %>%
#   dplyr::select(pidp, time, nutrition_quality) %>%
#   filter(pidp %in% raw.wave1) %>%
#   filter(nutrition_quality >= 0) %>%
#   group_by(time) %>%
#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.nut2 <- base.dat %>%
#   dplyr::select(pidp, time, nutrition_quality) %>%
#   filter(pidp %in% raw.wave1) %>%
#   group_by(time) %>%
#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
# 
# # Now plot
# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Nutrition Quality') +
#   xlab('Year') +
#   ylab('Nutrition Quality')
# 
# if (shall.we.save) {
#   ggsave(filename = 'nutrition_quality_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
#     nutrition_quality2)
```

@@

@@

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind)

@@

spaghetti_plot(spag, 'nkids_ind',
               save = shall.we.save,
               save.path = save.path)

>>>>

```{r}
raw.sf12.m <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12.m <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)

# sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
# spaghetti_plot(sf12.m.spag.sample, 'SF_12_MCS',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(sf12.m.spag.sample, 'SF_12_MCS',
#                save = shall.we.save,
#                save.path = save.path)

density_ridges(sf12.m.spag, "SF_12_MCS", 
               save = shall.we.save, 
               save.path = save.path)

rm(raw.sf12.m, base.sf12.m, sf12.m.spag, sf12.m.spag.sample)
```

## SF_12_PCS

```{r}
handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
```

```{r}
raw.sf12.p <- raw.dat %>%
  select(pidp, age, time, SF_12_PCS)
base.sf12.p <- base.dat %>%
  select(pidp, age, time, SF_12_PCS)

sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)

spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.p.spag, "SF_12_PCS", 
               save = shall.we.save, 
               save.path = save.path)

rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
```

@@

test.pidps <- raw.dat %>%
  select(pidp)

test.base <- base.dat %>%
  filter(pidp %in% test.pidps$pidp)

handover_boxplots(raw.dat, test.base, 'nutrition_quality')
handover_lineplots(raw.dat, test.base, 'nutrition_quality')
```

@@

## Tobacco

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'ncigs')
handover_lineplots(raw.dat, base.dat, 'ncigs')

test.pidps <- raw.dat %>%
  select(pidp)

test.base <- base.dat %>%
  filter(pidp %in% test.pidps$pidp)

handover_boxplots(raw.dat, test.base, 'ncigs')
handover_lineplots(raw.dat, test.base, 'ncigs')
```

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, ncigs)
base.nut <- base.dat %>%
  select(pidp, age, time, ncigs)

nut.spag <- rbind(raw.nut, base.nut)

spaghetti_plot(nut.spag, 'ncigs',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "ncigs",
               save = FALSE,
               save.path = save.path)

rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Alcohol (AUDITC)

```{r}
handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)

raw.2020.alc <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(auditc) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

## Physical Activity

```{r}
handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)

raw.2020.phys <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(active) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))
```

## Material Deprivation

```{r}
#handover_boxplots(raw.dat, base.dat, 'matdep')
#handover_lineplots(raw.dat, base.dat, 'matdep')
handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)

raw.dat$chron_disease <- as.factor(raw.dat$chron_disease)
raw.2020.cd <- raw.dat %>%
  select(time, chron_disease, age) %>%
  filter(time == 2020) %>%
  mutate(age_group = cut(age, 
                         breaks = c(0,20,30,40,50,60,70,80,90,100,120),
                         labels = c('16-19', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '100+'))) %>%
  group_by(age_group, chron_disease) %>%
  summarise(n = n()) %>%
  group_by(age_group) %>%
  mutate(prop = n / sum(n),
         perc = prop * 100)
  # mutate(prop = n() / sum(n),
  #        perc = prop * 100)

raw.2020.cd

ggplot(raw.2020.cd, aes(x = age_group, y = perc, group = chron_disease, colour = chron_disease, fill = chron_disease)) +
  geom_col(position = 'dodge') +
  xlab('Age Group') +
  ylab('Proportion')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, matdep) %>%
  filter(!matdep %in% miss.values)
base.s <- base.dat %>%
  select(pidp, age, time, matdep) %>%
  filter(!matdep %in% miss.values)

@@

spaghetti_plot(spag, 'matdep',
               save = shall.we.save,
               save.path = save.path)

## Chronic Disease

```{r}
handover_ordinal(raw.dat, base.dat, var = 'chron_disease', save = shall.we.save)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, chron_disease) %>%
  filter(!chron_disease %in% miss.values)
base.s <- base.dat %>%
  select(pidp, age, time, chron_disease) %>%
  filter(!chron_disease %in% miss.values)

spag$chron_disease <- as.numeric(spag$chron_disease)

spaghetti_plot(spag, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)

density_ridges(spag, 'chron_disease',
               save=shall.we.save, 
               save.path=save.path)

pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
spaghetti_plot(spag.sample, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)
